A General and Parallel Platform for Mining Co-Movement Patterns over Large-scale Trajectories

### 2017-04-26 Camera-Ready/sec6_experiment.tex
uptodate

%\vspace{-2mm}
\begin{table} [h]
\center
\begin{tabular}{|l|l|l|l|}
\hline
 \textbf{Attributes}& \textbf{Shopping} &  \textbf{GeoLife} &  \textbf{Taxi} \\ 
\hline 
\# objects  & 13,183 & 18,670 & 15,054\\ 
\hline
%\# average ts & 3,114  & 2,924 & 19,667 \\ 
%\hline
\# data points  & 41,052,242 & 54,594,696 & 296,075,837\\ 
\hline
\# snapshots  & 16,931 & 10,699 & 44,364\\ 
\hline
\# clusters  & 211,403  & 206,704& 536,804\\
\hline
avg. cluster size  & 171 & 223 & 484\\
\hline
\end{tabular}
%\vspace{-0.5em}
\caption{Statistics of datasets.}
%\vspace{-0.5em}
\label{exp:dataset}
\end{table}

\begin{table}[h]
\begin{tabular}{c|l|p{3.3cm}}
\hline 
\textbf{Param.} & \textbf{Meaning} & \textbf{Values} \\ 
\hline 
M & min  objects &  5, 10,  \textbf{15}, 20, 25 \\ 
\hline 
K & min duration & 120, 150, \textbf{180}, 210, 240 \\ 
\hline 
L & min local duration & 10, 20, \textbf{30}, 40,50 \\ 
\hline 
G & max gap & 10, 15, \textbf{20}, 25, 30 \\ 
\hline
$O_r$ & ratio of objects & 20\%,40\%,60\%,80\%,\textbf{100\%} \\ \hline
%$O_r$ & ratio of objects & 0.2, 0.4, 0.6, 0.8, 1 \\ \hline
$T_r$ & ratio of snapshots & 20\%,40\%,60\%,80\%,\textbf{100\%} \\ \hline
%$T_r$ & ratio of snapshots & 0.2, 0.4, 0.6, 0.8, 1 \\ \hline
N & number of machines & 1, 3, 5, 7, 9, \textbf{11}\\ 
\hline 
\end{tabular} 
%\vspace{-0.5em}
\caption{Parameters and their default values.}
 %\vspace{-0.5em}
\label{tbl:parameters}
\end{table}

@@

\textbf{Varying $O_r$}:Figures~\ref{exp:performance_vary} (e),(k),(q) present the performances with increasing number of moving objects. Both TRPM and SPARE take longer time to find patterns in a larger database. We can see that the performance gap between SPARE and TRPM is widened as more objects are involved, which shows SPARE is more scalable.

\textbf{Varying $T_r$}: Figures~\ref{exp:performance_vary} (f),(l),(r) present 
the performances with increasing number of snapshots. As $T_r$ increases, SPARE scales much better than TRPM due to its effective pruning in the temporal dimension.

@@

\begin{table}[h]
\centering
\begin{tabular}{|l|c|c|c|c|}
\hline
\multicolumn{1}{|c|}{\textbf{Dataset}} & \textbf{Method} 
& \textbf{Vcore-seconds} & \textbf{Memory} \\ \hline
\multirow{2}{*}{Shopping}              & TRPM           
                               & 90,859                 & 10,019               \\ 
                                       & SPARE           
                                                                      & 33,638                 & 8,613                \\ \hline
\multirow{2}{*}{Geolife}               & TRPM            
                              & 106,428                & 18,454               \\
                                       & SPARE            
                                                                     & 35,343                 & 14,369               \\ \hline
\multirow{2}{*}{Taxi}                  & TRPM            
                           & 503,460                & 51,691               \\ 
                                       & SPARE           
                                                                    & 68,580                & 35,912               \\ \hline
\end{tabular}
%\vspace{-0.5em}
\caption{Resources taken for TRPM and SPARE. Vcore-seconds is the aggregate of time spent in each core. Memory is the actual size (in MB) of RDDs.}
%\vspace{-0.5em}
\label{tbl:resource}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{|l|c|c|c|}
\hline 
\textbf{Dataset} & \textbf{Shopping} & \textbf{GeoLife} & \textbf{Taxi} \\ 
\hline 
Before pruning & 878,309 &  1,134,228 & 2,210,101 \\ 
\hline 
After pruning & 76,672 & 123,410 & 270,921 \\ 
\hline 
Prune ratio & 91.2\% & 89.1\% & 87.7\% \\ 
\hline 
\end{tabular} 
%\vspace{-0.5em}
\caption{Pruning power of SPARE.}
%\vspace{-0.5em}
\label{tbl:pruning}
\end{table}

@@

\begin{figure*}
\begin{minipage}{0.3\textwidth}
\includegraphics[width=\textwidth]{/exp/spare/detail1.eps}
 \caption{Cost breakdown of TRPM, SPARE-RD and SPARE.}
    \label{exp:wl}
\end{minipage}
\begin{minipage}{0.74\textwidth}
\centering
	 \begin{subfigure}[b]{0.32\textwidth}
        \includegraphics[width=\textwidth]{/exp/spare/scalability-shopping.eps}
        \caption{Shopping vary $N$}
    \end{subfigure} 
    \begin{subfigure}[b]{0.32\textwidth}
        \includegraphics[width=\textwidth]{/exp/spare/scalability-geolife.eps}
        \caption{GeoLife vary $N$}
    \end{subfigure} 
    \begin{subfigure}[b]{0.32\textwidth}
        \includegraphics[width=\textwidth]{/exp/spare/scalability-taxi.eps}
        \caption{Taxi vary $N$}
    \end{subfigure} 
 \caption{Comparisons among TRMP, SPARE, PLATOON and SWARM.}
 \label{exp:scalability}
\end{minipage}
\end{figure*}

\begin{table}[h]
\centering 
\begin{tabular}{|c|c|c|c|c|}
\hline
\multirow{2}{*}{\textbf{Dataset}} & \multicolumn{2}{c|}{\textbf{SPARE-RD}} & \multicolumn{2}{c|}{\textbf{SPARE}} \\ \cline{2-5} 
                         & Max        & Std. Dev.     & Max       & Std. Dev.      \\ \hline
Shopping                 & 295              & 41         & 237             & 21       \\ \hline
GeoLife                  & 484              & 108        & 341             & 56       \\ \hline
Taxi                     & 681              & 147        & 580             & 96       \\ \hline
\end{tabular}
%\vspace{-0.5em}
  \caption{Statistics of execution time (seconds) on all jobs.}
%\vspace{-0.5em}
  \label{tbl:strags}
\end{table}

>>>>

%\vspace{-2mm}
\begin{table} [t]
\centering
%\vspace{-0.5em}
\caption{Statistics of datasets.}
%\vspace{-0.5em}
\label{exp:dataset}
\begin{tabular}{|l|l|l|l|}
\hline
 \textbf{Attributes}& \textbf{Shopping} &  \textbf{GeoLife} &  \textbf{Taxi} \\ 
\hline 
\# objects  & 13,183 & 18,670 & 15,054\\ 
\hline
%\# average ts & 3,114  & 2,924 & 19,667 \\ 
%\hline
\# data points  & 41,052,242 & 54,594,696 & 296,075,837\\ 
\hline
\# snapshots  & 16,931 & 10,699 & 44,364\\ 
\hline
\# clusters  & 211,403  & 206,704& 536,804\\
\hline
avg. cluster size  & 171 & 223 & 484\\
\hline
\end{tabular}
\end{table}

\begin{table}[h]
%\vspace{-0.5em}
\caption{Parameters and their default values.}
 %\vspace{-0.5em}
\label{tbl:parameters}
\begin{tabular}{c|l|p{3.3cm}}
\hline 
\textbf{Param.} & \textbf{Meaning} & \textbf{Values} \\ 
\hline 
M & min  objects &  5, 10,  \textbf{15}, 20, 25 \\ 
\hline 
K & min duration & 120, 150, \textbf{180}, 210, 240 \\ 
\hline 
L & min local duration & 10, 20, \textbf{30}, 40,50 \\ 
\hline 
G & max gap & 10, 15, \textbf{20}, 25, 30 \\ 
\hline
$O_r$ & ratio of objects & 20\%,40\%,60\%,80\%,\textbf{100\%} \\ \hline
%$O_r$ & ratio of objects & 0.2, 0.4, 0.6, 0.8, 1 \\ \hline
$T_r$ & ratio of snapshots & 20\%,40\%,60\%,80\%,\textbf{100\%} \\ \hline
%$T_r$ & ratio of snapshots & 0.2, 0.4, 0.6, 0.8, 1 \\ \hline
N & number of machines & 1, 3, 5, 7, 9, \textbf{11}\\ 
\hline 
\end{tabular} 
\end{table}

@@

\textbf{Varying $O_r$}: Figures~\ref{exp:performance_vary} (e),(k),(q) present the performances with increasing number of moving objects. Both TRPM and SPARE take longer time to find patterns in a larger database. We can see that the performance gap between SPARE and TRPM is widened as more objects are involved, which shows SPARE is more scalable.

\textbf{Varying $T_r$}: Figures~\ref{exp:performance_vary} (f),(l),(r) present 
the performances with increasing number of snapshots. When $T_r$ increases, SPARE scales much better than TRPM due to its effective pruning in the temporal dimension.

@@

\begin{table}[h]
\centering
%\vspace{-0.5em}
\caption{Resources taken for TRPM and SPARE. Vcore-seconds is the aggregate of time spent in each core. Memory is the actual size (in MB) of RDDs.}
%\vspace{-0.5em}
\label{tbl:resource}
\begin{tabular}{|l|c|c|c|c|}
\hline
\multicolumn{1}{|c|}{\textbf{Dataset}} & \textbf{Method} 
& \textbf{Vcore-seconds} & \textbf{Memory} \\ \hline
\multirow{2}{*}{Shopping}              & TRPM           
                               & 90,859                 & 10,019               \\ 
                                       & SPARE           
                                                                      & 33,638                 & 8,613                \\ \hline
\multirow{2}{*}{Geolife}               & TRPM            
                              & 106,428                & 18,454               \\
                                       & SPARE            
                                                                     & 35,343                 & 14,369               \\ \hline
\multirow{2}{*}{Taxi}                  & TRPM            
                           & 503,460                & 51,691               \\ 
                                       & SPARE           
                                                                    & 68,580                & 35,912               \\ \hline
\end{tabular}
\end{table}

@@

\begin{table}[h]
\centering
%\vspace{-0.5em}
\caption{Pruning power of SPARE.}
%\vspace{-0.5em}
\label{tbl:pruning}
\begin{tabular}{|l|c|c|c|}
\hline 
\textbf{Dataset} & \textbf{Shopping} & \textbf{GeoLife} & \textbf{Taxi} \\ 
\hline 
Before pruning & 878,309 &  1,134,228 & 2,210,101 \\ 
\hline 
After pruning & 76,672 & 123,410 & 270,921 \\ 
\hline 
Prune ratio & 91.2\% & 89.1\% & 87.7\% \\ 
\hline 
\end{tabular} 
\end{table}

@@

\begin{figure*}
\begin{minipage}{0.3\textwidth}
\includegraphics[width=\textwidth]{/exp/spare/detail1.eps}
 \caption{Cost breakdown of TRPM, SPARE-RD and SPARE.}
    \label{exp:wl}
\end{minipage}
\begin{minipage}{0.7\textwidth}
\centering
	 \begin{subfigure}[b]{0.32\textwidth}
        \includegraphics[width=\textwidth]{/exp/spare/scalability-shopping.eps}
        \caption{Shopping vary $N$}
    \end{subfigure} 
    \begin{subfigure}[b]{0.32\textwidth}
        \includegraphics[width=\textwidth]{/exp/spare/scalability-geolife.eps}
        \caption{GeoLife vary $N$}
    \end{subfigure} 
    \begin{subfigure}[b]{0.32\textwidth}
        \includegraphics[width=\textwidth]{/exp/spare/scalability-taxi.eps}
        \caption{Taxi vary $N$}
    \end{subfigure} 
 \caption{Comparisons among TRMP, SPARE, PLATOON and SWARM.}
 \label{exp:scalability}
\end{minipage}
\end{figure*}

\begin{table}[h]
\centering 
%\vspace{-0.5em}
  \caption{Statistics of execution time (seconds) on all jobs.}
%\vspace{-0.5em}
  \label{tbl:strags}
\begin{tabular}{|c|c|c|c|c|}
\hline
\multirow{2}{*}{\textbf{Dataset}} & \multicolumn{2}{c|}{\textbf{SPARE-RD}} & \multicolumn{2}{c|}{\textbf{SPARE}} \\ \cline{2-5} 
                         & Max        & Std. Dev.     & Max       & Std. Dev.      \\ \hline
Shopping                 & 295              & 41         & 237             & 21       \\ \hline
GeoLife                  & 484              & 108        & 341             & 56       \\ \hline
Taxi                     & 681              & 147        & 580             & 96       \\ \hline
\end{tabular}
\end{table}
